\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-17 jss/article.tex
sigma -> V

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\sigma^{2}_{j}/(\sigma^{2}_{j} + A),~j=1, \ldots, 8$, are called shrinkages.

@@

\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\sigma^{2}/(\sigma^{2}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
\\

>>>>

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})V_{j}),
\end{equation}
where $B_{j}\equiv V_{j}/(V_{j} + A),~j=1, \ldots, 8$, are called shrinkages.

@@

\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv V_{j}/(V_{j}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
\\
